---
title: "Lab3-Gapminder.Rmd"
author: "Ivonne Kienast"
date: "2/26/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data

ggplot to visually explore global trends in public health and economics compiled by the Gapminder project. This project was pioneered by Hans Rosling, who is famous for describing the prosperity of nations over time through famines, wars and other historic events.

```{r}
# install.packages("dslabs")
library(dslabs)
library(tidyverse)
?gapminder

gap2011<- gapminder %>%
  as_tibble() %>%
  filter(year == 2011)
```

## Life expectancy

Patterns in life expectancy

```{r}
gap2011 %>%
  ggplot(aes(x=gdp/population, y=life_expectancy, size=population, color = continent)) +
  geom_point()
```

<br>
<br>
#### Relation of life expectancy to infant mortality
```{r}
gap2011 %>%
  ggplot(aes(x=life_expectancy,y= infant_mortality , color = continent))+
  geom_point()
```

<br>
<br>
#### Relation of life exptectancy to fertilty
```{r}
gap2011 %>%
  ggplot(aes(x= life_expectancy, y= fertility, color = continent))+
  geom_point()
```


#### Testing group_by
```{r}
#group_by(gapminder, life_expectancy, infant_mortality, fertility, population, gdp) %>%
#  summarize(mean_gdp) %>%
#  ggplot(aes(x=)) +
#  geom_point() +
#  geom_line() +
#  facet_wrap
```


## Fertility


```{r}
gap2011 %>%
  ggplot(aes(x= gdp/population, y= fertility, color = continent))+
  geom_point()
```

#### Comparing fertility to infant mortality

```{r}
gap2011 %>%
  ggplot(aes(x= fertility, y= infant_mortality, color = continent))+
  geom_point()
```



## Infant Mortality

```{r}
gap2011 %>%
  ggplot(aes(x= gdp/population, y= infant_mortality, color = continent))+
  geom_point()
```

